### 2018-03-21 franck-hertz/paper.tex
More intro

	Primary components of the experimental setup include a filament used for emitting electrons, electron-accelerating grids and an anode collecting the electrons; all of these are contained in a mercury vapor filled tube. Additionally, power supplies for heating the filament and accelerating the electrons, an oven for heating the tube, an electrometer and a voltmeter were used. The required apparatus are shown below.

	\paperfig{Setup}{\pdf{setup}}{Devices used in the experiment prior to wiring. The final apparatus was connected using the schematic circuit diagram further below.}

>>>>

	Primary components of the experimental setup include a filament used for emitting electrons, electron-accelerating grids and an anode collecting the electrons; all of these are contained in a mercury vapor filled tube. Additionally, power supplies for heating the filament and accelerating the electrons, an oven for heating the tube, an electrometer and a voltmeter were used. The required devices are shown below.

	\paperfig{Setup}{\vspace{-1em} \pdf{setup} \vspace{-3em}}{Apparatus used in the experiment prior to wiring. The final apparatus was connected using the schematic circuit diagram further below. The panel supports four DC voltages with functions explained below.}
